LAGOS lake depth

### 2021-12-07 figures/02_depth_model.Rmd
format fig 5

ggplot() +
  geom_point(data = dt_imp, aes(percent_inc_mse, variable, color = model)) +
  labs(color = "slope-distance\nmeasure") +
  geom_hline(linetype = 3, size = 1, colour = "gray",
    yintercept = 1:nlevels(dt_imp$variable)) +
  theme(text = element_text(family = "Times"),
    panel.background = element_blank(), panel.grid = element_blank(),
    panel.border = element_rect(fill = NA), # legend.position = "none",
    axis.title.x = element_text(family = "sans", face = "bold",
      vjust = -0.5, size = 10),
    axis.text = element_text(family = "sans", size = 9,
      color = "black"),
    legend.key = element_blank()) +
  ylab("") + xlab("Percent Increase in Mean Square Error")
```

>>>>

ggplot() +
  geom_point(data = dt_imp, aes(percent_inc_mse, variable, color = model)) +
  labs(color = "slope-distance\nmeasure") +
  geom_hline(linetype = 3, size = 1, colour = "gray",
    yintercept = 1:nlevels(dt_imp$variable)) +
  theme(text = element_text(family = "Times"),
    panel.background = element_blank(), panel.grid = element_blank(),
    panel.border = element_rect(fill = NA), # legend.position = "none",
    axis.title.x = element_text(family = "sans", face = "bold",
      vjust = -0.5, size = 10),
    axis.text = element_text(family = "sans", size = 9,
      color = "black"),
    legend.key = element_blank()) +
  ylab("") + xlab("Percent increase in mean square error")
```
